Figures

### 2019-12-29 manuscript/figures.Rmd
fill out figure pipeline

# exploratory analyses

# hypsography classification figure (panelized by state)

>>>>

<!-- # exploratory analyses -->

```{r heatmap, fig.cap = "Heatmap caption.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_heatmap-1.pdf")
```

<!-- # hypsography classification figure (panelized by state) -->
```{r hypsography, fig.cap = "Hypsography classification by state.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_hypsography-1.pdf")
```
